### 2025-09-04 draft.qmd
20250904 - herding behavior

>>>>

Engaging in herding behavior—by following a run, i.e., drafting a player at the same position as previous drafters—can be harmful.
For instance, if the run on Quarterbacks is premature, it can lead the "herd" (i.e., the managers who draft a Quarterback after the previous drafters) to spend important draft capital that could have yielded more impactful players at other positions.
However, engaging in herding behavior is not always harmful.
Herding behavior can be rational if a) there is positional scarcity, or if b) not drafting a player at that position would leave with you without a serviceable option at that position.
Position scarcity refers to the [dropoff](#sec-fantasyValueDropoff) of fantasy points after the top tier of a position—i.e., how steeply player value declines as you move down the rankings, as depicted in @sec-expectedPointsByPositionRank.
For instance, Quarterbacks and Tight Ends tend to show greater positional scarcity than Running Backs and Wide Receivers.
That is, there tend to be fewer elite options available at Quarterback and Tight End than at Running Back and Wide Receiver.
So, in leagues that have two Quarterbacks on the starting roster or a superflex position (i.e., QB/RB/WR/TE), herding due to positional scarcity can be strategically sound.
In general, though, it may be optimal to either a) be at the beginning of a run (i.e., to be the manager who drafts a player, which leads to a run on that position) to secure a scarce, elite option, or b) to avoid the run altogether (by waiting to draft that position later), rather than joining the run in the middle or at the end.
